Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-30 README.Rmd
Cleaned up land ID description
updated to do list

- Finish documenting the identification of the training data for rtrees in research journals (including LIME explanations from different training datasets/models)
- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit

@@

- **`r names(bullet_train)[1]`**: ID number associated with the bullet-land signature comparison.
- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrelnumber-bulletnumber-landnumber".

>>>>

- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit

@@

- **`r names(bullet_train)[1]`**: ID number associated with the bullet-land signature comparison.
- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrel-bullet-land".
